\chapter{Units and Measurement}

\begin{problem}[Kilometers per hour]\label{problem_3_1}
    A car os driving at 144 km/h. Find the velocity in m/s
\end{problem}


\begin{problem}[Miles per hour]\label{problem_3_2}
    You car speedometer is showing both km/h and mph, miles per hour. 1 miles is 1609.34 m.
    \begin{enumerate}
        \item If you speedometer is showing 70 km/h. What does it show in mph?
        \item If you speedometer is showing 55 mph. What does it show in km/h
    \end{enumerate}
\end{problem}


\begin{problem}[Acceleration of gravity]\label{problem_3_3}
    The acceleration of gravity is approximately $g=9.8 \ m/s^2$.
    \begin{enumerate}
        \item Find the acceleration of gravity in feet per second squared, $ft/s^{2}$. 1 foot is 0.3048 m.
        \item Find the acceleration of gravity in kilometers per hour  squared, $km/h^{2}$.
    \end{enumerate}
\end{problem}


\begin{problem}[Bacterial volume]\label{problem_3_4}
    A bacteria is like a cylinder with legnth $4 \mu m$ and radius $1 \ \mu m$.
    \begin{enumerate}
        \item Find its volume in $\mu m^{3}$.
        \item Find its volume in $m^{3}$.
        \item Find its volume in liters.
    \end{enumerate}
\end{problem}


\begin{problem}[Ruler length]\label{problem_3_5}
    You have a platinum-iridium ruler that you have measured to be 0.11236 m using a high precision method. You use the ruler to measure the length of your desk, and find that the ruler fits about 20 times across the desk. What is  the length of your desk?
\end{problem}


\begin{problem}[Sphere mass and volume]\label{problem_3_6}
    A small steel sphere has a radius of 1.2 mm. 
    \begin{enumerate}
        \item What is the volume of the sphere?
        \item The density of the particular steel alloy used is $\rho = 7782 kg/m^{3}$. What is the mass of the sphere?
    \end{enumerate}
\end{problem}


\begin{problem}[Laserlength]\label{problem_3_7}
    You use a laser distance measurer to measure the distance from one wall to another in your house. It reads 11.2 m. As you walk across to the other wall, you see that there is a small protrusion from the wall. Using your tape measure, you find that the protrusion is 5 mm high. What is the distance from the other wall to the protrusion?
\end{problem}


\begin{problem}[Salmon speed]\label{problem_3_8}
    You have designed a special circuit to measure the swimming speed of a salmon. The circuit has a length of 62.8 m. You measure the time a salmon takes to swim one lap to be 20.6 s.
    \begin{enumerate}
        \item What is the swimming speed of a salmon? \\
              Your assistant insists that you would get better precision if you instead measured the time the salmon took to swim 10 rounds. You find that the salmon uses 206.0 s to swim 10 rounds.
        \item What is the speed of the salmon?
        \item Does this produce better accuracy? Can you give other examples of situations where this strategy would improve the accuracy?
    \end{enumerate}
\end{problem}